Examining equity in accessibility to bike share: a balanced floating catchment area approach

### 2021-10-14 Bike-share-spatial-equity/Response-to-Reviewers-R3.Rmd

---
title: "Response to Reviewers"
author: ""
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
---

We would like to express our gratitude to the editors and anonymous reviewers for their time and attention to our submission.

## Reviewer #1:

This paper is ready for publication. I don't have any more comments.

\textcolor{blue}{Thank you for your generous feedback to improve this paper.}

## Reviewer #3:

Thank you for revising in response to my prior comments. Due to an editorial error, I missed a round of feedback so will keep my comments brief and mainly reiterate some prior points.

\textcolor{blue}{Thank you again for your suggestions to improve the paper.}

Because travel is derived from a demand for activity participation, I still do not believe that you are quantifying accessibility in this paper. No one gets to a bike share station consumes the service of bike share and ends their trip. The bike share is a means to an end. You overstate your position on p. 6, l. 20 when you claim that the docking stations are an amenity because they offer a transportation service. Again – people consume travel to reach destinations where they can undertake activities. This fact must be noted in the study limitations.

\textcolor{blue}{Words go here.}

Many of the maps are still very difficult to interpret. I previously suggested plotting the difference in accessibility (for example for Figures 4-6) to make the differences easy to discern. Currently it’s very difficult to detect any changes in the maps at all. I also suggested experimenting with a discrete scale. This might also help to make the differences easier to discern without needing an explicit map of difference. All units in the map legends need to be spelled out (e.g., “accessibility (racks/person)”) and use plain English with any acronyms defined (e.g., for los_inflation and accessibility_inflation). The discordance between the label for Figure 7 “deflation” and legend “inflation” should be resolved. Scale bar and north arrow only need to be shown once on the small multiples maps.

\textcolor{blue}{Words go here.}

### 2021-10-14 Bike-share-spatial-equity/Bike-share-spatial-equity.Rmd
Revisions after reviewer comments R2

Chen et al. [-@chenExploringEquityPerformance2019] distinguish two types of equity related to bike share, horizontal and vertical, based on the work of Delbosc and Currie [@delboscUsingLorenzCurves2011]. Horizontal equity leads to balanced or equal distribution of accessibility and costs for all similar groups, while vertical equity would involve greater and targeted access for under-represented or disadvantaged populations [@chenExploringEquityPerformance2019]. Both are of interest to researchers and transportation planners since they are often linked in that advantage, or conversely disadvantage, has spatial patterns. Bike share equity programs [see @trec2019; @@howlandCurrentEffortsMake2017] can be considered efforts to improve vertical equity since they favour groups that have benefited less from PBSPs through the placement of stations or equitable fee structures.

@@

To obtain population at sub-census geography levels, we used pycnophylactic interpolation [@toblerSmoothPycnophylacticInterpolation1979]. We obtained population data from the 2016 Census of Canada for dissemination areas (DA), which is the smallest publicly available census geography in Canada. These zonal values of the population were interpolated to smaller polygons that are 50-by-50 m in size. Pycnophylactic interpolation involves smoothing out the population from each DA while preserving total volume [see Figure \ref{fig:da-population}]. When interpolating the population at this high level of resolution, it is important to ensure that population numbers were not allocated to areas where people do not live in Hamilton (for example, to parks or large institutional buildings, etc.). To do so, we retrieved shapefiles for various geographic features from Open Hamilton. Next, we removed these features from the PBSP core service area and used pycnophylactic interpolation to disaggregate and reallocate population within the remaining area [see Figure \ref{fig:interpolated-population}].

```{r interpolated-population, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Interpolated population in Hamilton Bike Share's core service area (outlined in blue) and within 30 minutes of walking to the core service area. Each population cell is 50-by-50 m in size. The downtown area is outlined in dark green."}
ggplot() + 
  geom_sf(data = cropped_da,
          fill = "gray",
          color = NA) + 
  #geom_sf(data = population_50x50,
  #        aes(color = population)) +
   #scale_fill_gradient(colours = "YlOrRd") +
  geom_tile(data = cbind(st_drop_geometry(population_50x50), 
                         st_coordinates(population_50x50)),
            aes(x = X, 
                y = Y, 
                fill = population)) +
  scale_fill_distiller(palette = "YlOrRd", 
                        direction = 1) +
  geom_sf(data = sobi_service,
          fill = NA,
          colour = "blue") +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank()) +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.25, "in"), pad_y = unit(0.20, "in"),
        style = north_arrow_fancy_orienteering)
```

@@

ggplot() +
  geom_sf(data = population_50x50,
          color = "gray") +
  #geom_sf(data = accessibility %>%
  #          dplyr::filter(threshold == "3 min"),
  #        aes(color = accessibility)) +
  #scale_color_distiller(palette = "PuRd", 
  #                      direction = 1) +
  geom_tile(data = cbind(st_drop_geometry(accessibility_3min), st_coordinates(accessibility_3min)),
            aes(x = X, y = Y, fill = accessibility)) +
  scale_fill_distiller(palette = "PuRd", direction = 1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ threshold)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  # geom_sf(data =  sobi_hubs %>% 
  #           dplyr::filter(hub_type == "ERI"), 
  #         size = 1.5, shape = 21, 
  #         fill = "green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)

@@

### 5.1.2. Average Threshold

@@

```{r figure-7, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Accessibility at 5 minutes walk (average threshold) compared between current system with equity stations and the original system without equity stations."}
#accessibility plot for current system with equity stations at 5 minutes walk
accessibility_5min <- accessibility %>% 
  dplyr::filter(threshold == "5 min")

ggplot() +
  geom_sf(data = population_50x50,
          color = "gray") +
  #geom_sf(data = accessibility %>%
  #          dplyr::filter(threshold == "5 min"),
  #        aes(color = accessibility)) +
  #scale_color_distiller(palette = "PuRd", 
  #                      direction = 1) +
  geom_tile(data = cbind(st_drop_geometry(accessibility_5min), st_coordinates(accessibility_5min)),
            aes(x = X, y = Y, fill = accessibility)) +
  scale_fill_distiller(palette = "PuRd", 
                       direction = 1,
                       trans = "log",
                       breaks = c(0.001, 0.02, 0.4, 8)) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ threshold)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  # geom_sf(data =  sobi_hubs %>% 
  #           dplyr::filter(hub_type == "ERI"), 
  #         size = 1.5, shape = 21, 
  #         fill = "green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)
```

### 5.1.3. Maximum Threshold

@@

```{r figure-8, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Accessibility at 10 minutes walk (maximum threshold) compared between current system with equity stations and the original system without equity stations."}
#accessibility plot for current system with equity stations at 10 minutes walk
accessibility_10min <- accessibility %>% 
  dplyr::filter(threshold == "10 min")

ggplot() +
  geom_sf(data = population_50x50,
          color = "lightgray") +
  #geom_sf(data = accessibility %>%
  #          dplyr::filter(threshold == "10 min"),
  #        aes(color = accessibility)) +
  #scale_color_distiller(palette = "PuRd", 
  #                      direction = 1) +
  geom_tile(data = cbind(st_drop_geometry(accessibility_10min), st_coordinates(accessibility_10min)),
            aes(x = X, y = Y, fill = accessibility)) +
  scale_fill_distiller(palette = "PuRd",
                       direction = 1,
                       trans = "log",
                       breaks = c(0.00004, 0.0003, 0.002)) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ threshold)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  # geom_sf(data =  sobi_hubs %>% 
  #           dplyr::filter(hub_type == "ERI"), 
  #         size = 1.5, shape = 21, 
  #         fill = "green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)
```

@@

```{r figure-9, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Accessibility at 15 minutes walk (extreme threshold) compared between current system with equity stations and the original system without equity stations."}
#accessibility plot for current system with equity stations at 15 minutes walk
accessibility_15min <- accessibility %>% 
  dplyr::filter(threshold == "15 min")

ggplot() +
  geom_sf(data = population_50x50,
          color = "lightgray") +
  #geom_sf(data = accessibility %>%
  #          dplyr::filter(threshold == "15 min"),
  #        aes(color = accessibility)) +
  #scale_color_distiller(palette = "PuRd", 
  #                      direction = 1) +
  geom_tile(data = cbind(st_drop_geometry(accessibility_15min), st_coordinates(accessibility_15min)),
            aes(x = X, y = Y, fill = accessibility)) +
  scale_fill_distiller(palette = "PuRd", 
                       direction = 1,
                       trans = "log",
                       breaks = c(0.000006, 0.00005, 0.0003)) +
  geom_sf(data = sobi_service,
          fill = NA) +

  facet_grid(system ~ threshold)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  # geom_sf(data =  sobi_hubs %>% 
  #           dplyr::filter(hub_type == "ERI"), 
  #         size = 1.5, shape = 21, 
  #         fill = "green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)
```

@@

```{r figure-10, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Deflation of level of service at 5 minutes walk (average threshold) in the current system with equity stations."}
ggplot() +
  geom_sf(data = population_50x50,
          color = "gray") +
  geom_sf(data = los_inflation,
            aes(size = los_inflation, color = los_inflation)) +
  scale_color_distiller(palette = "PuRd", direction = 1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)
```

```{r figure-11, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Inflation of accessibility at 5 minutes walk (average threshold) in the current system with equity stations."}
ggplot() +
  geom_sf(data = population_50x50,
          color = "gray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_inflation), st_coordinates(accessibility_inflation)),
            aes(x = X, y = Y, fill = accessibility_inflation)) +
  scale_fill_distiller(palette = "PuRd", direction = 1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)
```

@@

bi_map_3_all <- ggplot() +
  geom_sf(data = data_map %>%
            st_buffer(dist = 25, endCapStyle = "SQUARE"),
          mapping = aes(fill = bi_class), 
          color = NA,
          show.legend = FALSE) +
  geom_sf(data = cropped_da,
          fill = NA,
          color = "lightgrey") +
  geom_sf(data = sobi_service, 
          fill = NA,
          color = "blue") +
  ggtitle("All stations") +
  bi_scale_fill(pal = "GrPink", 
                dim = 3) +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in")) +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        plot.title = element_text(hjust=0.5))

@@

>>>>

Chen et al. [-@chenExploringEquityPerformance2019] distinguish two types of equity related to bike share, horizontal and vertical, based on the work of Delbosc and Currie [@delboscUsingLorenzCurves2011]. Horizontal equity leads to balanced or equal distribution of accessibility and costs for all similar groups, while vertical equity would involve greater and targeted access for under-represented or disadvantaged populations [@chenExploringEquityPerformance2019]. Both are of interest to researchers and transportation planners since they are often linked in that advantage, or conversely disadvantage, has spatial patterns. Bike share equity programs [see @trec2019; @howlandCurrentEffortsMake2017] can be considered efforts to improve vertical equity since they favour groups that have benefited less from PBSPs through the placement of stations or equitable fee structures.

@@

To obtain population at sub-census geography levels, we used pycnophylactic interpolation [@toblerSmoothPycnophylacticInterpolation1979]. We obtained population data from the 2016 Census of Canada for dissemination areas (DA), which is the smallest publicly available census geography in Canada. These zonal values of the population were interpolated to smaller polygons that are 50-by-50 m in size. Pycnophylactic interpolation involves smoothing out the population from each DA while preserving total volume. When interpolating the population at this high level of resolution, it is important to ensure that population numbers are not allocated to areas where people do not live in Hamilton (for example, to parks or large institutional buildings, etc.). To do so, we retrieved shapefiles for various geographic features from Open Hamilton. Next, we removed these features from the PBSP core service area and used pycnophylactic interpolation to disaggregate and reallocate population within the remaining area [see Figure \ref{fig:interpolated-population}].

```{r interpolated-population, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Interpolated population in Hamilton Bike Share's core service area (outlined in blue) and within 30 minutes of walking to the core service area. Each population cell is 50-by-50 m in size. The downtown area is outlined in dark green."}
ggplot() + 
  geom_sf(data = cropped_da,
          fill = "gray",
          color = NA) + 
  geom_tile(data = cbind(st_drop_geometry(population_50x50), 
                         st_coordinates(population_50x50)),
            aes(x = X, 
                y = Y, 
                fill = population)) +
  scale_fill_distiller(name = "Population",
                       palette = "YlOrRd",
                       direction = 1) +
  geom_sf(data = sobi_service,
          fill = NA,
          colour = "blue") +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank()) +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.25, "in"), pad_y = unit(0.20, "in"),
        style = north_arrow_fancy_orienteering)
```

@@

ggplot() +
  geom_sf(data = population_50x50,
          color = "gray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_3min), st_coordinates(accessibility_3min)),
            aes(x = X, y = Y, fill = accessibility)) +
  scale_fill_distiller(palette = "PuRd", direction = 1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ threshold)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)

@@

### 5.1.2. Medium Threshold

@@

```{r figure-7-a, include=FALSE}
#accessibility plot for current system with equity stations at 5 minutes walk
accessibility_5min <- accessibility %>% 
  dplyr::filter(threshold == "5 min",
                system == "All stations") %>%
  mutate(accessibility = cut(accessibility,
                             breaks = c(-Inf, 0.001, 0.02, 0.4, 8, Inf), 
                             labels=c("<0.001", "0.001-0.02", "0.02-0.4", "0.4-8", ">8")),
         accessibility = factor(accessibility,
                                levels = c(">8", "0.4-8", "0.02-0.4", "0.001-0.02", "<0.001"),
                                ordered = TRUE))

acc_5_all <- ggplot() +
  geom_sf(data = population_50x50,
          color = "gray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_5min), 
                         st_coordinates(accessibility_5min)),
            aes(x = X, y = Y, fill = accessibility)) +
  scale_fill_brewer(name = "Accessibility\n(racks/person)",
                    palette = "PuRd", 
                    direction = -1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ .)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)

# Extract the legend
acc_5_legend <- cowplot::get_legend(acc_5_all)
```

```{r figure-7-b, include=FALSE}
#accessibility plot for current system with equity stations at 5 minutes walk
accessibility_5min <- accessibility %>% 
  dplyr::filter(threshold == "5 min",
                system == "Conventional") %>%
  mutate(accessibility = cut(accessibility,
                             breaks = c(-Inf, 0.001, 0.02, 0.4, 8, Inf), 
                             labels = c("<0.001", "0.001-0.02", "0.02-0.4", "0.4-8", ">8")),
         accessibility = factor(accessibility,
                                levels = c(">8", "0.4-8", "0.02-0.4", "0.001-0.02", "<0.001"),
                                ordered = TRUE))

acc_5_conv <- ggplot() +
  geom_sf(data = population_50x50,
          color = "gray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_5min),
                         st_coordinates(accessibility_5min)),
            aes(x = X, 
                y = Y, 
                fill = accessibility)) +
  scale_fill_brewer(name = "Accessibility\n(racks/person)",
                    palette = "PuRd", 
                    direction = -1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ .)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"))
```

```{r figure-7, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Accessibility at 5 minutes walk (average threshold) compared between current system with equity stations and the original system without equity stations."}
ggdraw() + 
  draw_plot(acc_5_all + 
              theme(legend.position = "none"), 
            0.00, 0.5, 1, 0.5) + 
  draw_plot(acc_5_conv + 
              theme(legend.position = "none"), 0.00, 0.0, 1, 0.5) + 
  draw_plot(acc_5_legend, 0.01, 0.4, 0.2, 0.2)
```

### 5.1.3. High Threshold

@@

```{r figure-8-a, include=FALSE}
#accessibility plot for current system with equity stations at 10 minutes walk
accessibility_10min <- accessibility %>% 
  dplyr::filter(threshold == "10 min",
                system == "All stations")  %>%
  mutate(accessibility = cut(accessibility,
                             breaks = c(-Inf, 0.00004, 0.0003, 0.002, Inf), 
                             labels = c("<0.00004", "0.00004-0.0003", "0.0003-0.002", ">0.002")),
         accessibility = factor(accessibility,
                                levels = c( ">0.002", "0.0003-0.002", "0.00004-0.0003", "<0.00004"),
                                ordered = TRUE))

acc_10_all <- ggplot() +
  geom_sf(data = population_50x50,
          color = "lightgray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_10min), 
                         st_coordinates(accessibility_10min)),
            aes(x = X, 
                y = Y, 
                fill = accessibility)) +
  scale_fill_brewer(name = "Accessibility\n(racks/person)",
                    palette = "PuRd",
                    direction = -1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ .)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)

# Extract the legend
acc_10_legend <- cowplot::get_legend(acc_10_all)
```

```{r figure-8-b, include=FALSE}
#accessibility plot for current system without equity stations at 10 minutes walk
accessibility_10min <- accessibility %>% 
  dplyr::filter(threshold == "10 min",
                system == "Conventional")  %>%
  mutate(accessibility = cut(accessibility,
                             breaks = c(-Inf, 0.00004, 0.0003, 0.002, Inf), 
                             labels = c("<0.00004", "0.00004-0.0003", "0.0003-0.002", ">0.002")),
         accessibility = factor(accessibility,
                                levels = c( ">0.002", "0.0003-0.002", "0.00004-0.0003", "<0.00004"),
                                ordered = TRUE))

acc_10_conv <- ggplot() +
  geom_sf(data = population_50x50,
          color = "lightgray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_10min), 
                         st_coordinates(accessibility_10min)),
            aes(x = X, 
                y = Y, 
                fill = accessibility)) +
  scale_fill_brewer(name = "Accessibility\n(racks/person)",
                    palette = "PuRd",
                    direction = -1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ .)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"))
```

```{r figure-8, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Accessibility at 10 minutes walk (maximum threshold) compared between current system with equity stations and the original system without equity stations."}
ggdraw() + 
  draw_plot(acc_10_all + 
              theme(legend.position = "none"), 
            0.00, 0.5, 1, 0.5) + 
  draw_plot(acc_10_conv + 
              theme(legend.position = "none"), 0.00, 0.0, 1, 0.5) + 
  draw_plot(acc_10_legend, 0.01, 0.4, 0.2, 0.2)
```

@@

```{r figure-9-a, include=FALSE}
#accessibility plot for current system with equity stations at 15 minutes walk
accessibility_15min <- accessibility %>% 
  dplyr::filter(threshold == "15 min",
                system == "All stations")  %>%
  mutate(accessibility = cut(accessibility,
                             breaks = c(-Inf, 0.000006, 0.00005, 0.0003, Inf), 
                             labels = c("<0.000006", "0.000006-0.00005", "0.00005-0.0003", ">0.0003")),
         accessibility = factor(accessibility,
                                levels = c( ">0.0003", "0.00005-0.0003", "0.000006-0.00005", "<0.000006"),
                                ordered = TRUE))

acc_15_all <- ggplot() +
  geom_sf(data = population_50x50,
          color = "lightgray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_15min), st_coordinates(accessibility_15min)),
            aes(x = X, y = Y, fill = accessibility)) +
  scale_fill_brewer(name = "Accessibility\n(racks/person)",
                    palette = "PuRd", 
                    direction = -1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ .)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)

# Extract the legend
acc_15_legend <- cowplot::get_legend(acc_15_all)
```

```{r figure-9-b, include=FALSE}
#accessibility plot for current system with equity stations at 15 minutes walk
accessibility_15min <- accessibility %>% 
  dplyr::filter(threshold == "15 min",
                system == "Conventional")  %>%
  mutate(accessibility = cut(accessibility,
                             breaks = c(-Inf, 0.000006, 0.00005, 0.0003, Inf), 
                             labels = c("<0.000006", "0.000006-0.00005", "0.00005-0.0003", ">0.0003")),
         accessibility = factor(accessibility,
                                levels = c( ">0.0003", "0.00005-0.0003", "0.000006-0.00005", "<0.000006"),
                                ordered = TRUE))

acc_15_conv <- ggplot() +
  geom_sf(data = population_50x50,
          color = "lightgray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_15min), st_coordinates(accessibility_15min)),
            aes(x = X, y = Y, fill = accessibility)) +
  scale_fill_brewer(name = "Accessibility\n(racks/person)",
                    palette = "PuRd", 
                    direction = -1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ .)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"))
```

```{r figure-9, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Accessibility at 15 minutes walk (extreme threshold) compared between current system with equity stations and the original system without equity stations."}
ggdraw() + 
  draw_plot(acc_15_all + 
              theme(legend.position = "none"), 
            0.00, 0.5, 1, 0.5) + 
  draw_plot(acc_15_conv + 
              theme(legend.position = "none"), 0.00, 0.0, 1, 0.5) + 
  draw_plot(acc_15_legend, 0.01, 0.4, 0.2, 0.2)
```

@@

```{r figure-10, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Deflation of level of service at 5 minutes walk (average threshold) in the current system with equity stations."}
ggplot() +
  geom_sf(data = population_50x50,
          color = "gray") +
  geom_sf(data = los_inflation,
            aes(size = los_inflation, color = los_inflation)) +
  scale_color_distiller(name = "Deflation of Level of Service",
                        palette = "PuRd", 
                        direction = 1) +
  guides(size = guide_legend(title = "")) +
  geom_sf(data = sobi_service,
          fill = NA) +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", 
                   width_hint = 0.4,
                   pad_x = unit(0.4, "in"), 
                   pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tr", 
                         which_north = "true", 
        pad_x = unit(0.0, "in"), 
        pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)
```

```{r figure-11, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Inflation of accessibility at 5 minutes walk (average threshold) in the current system with equity stations."}
ggplot() +
  geom_sf(data = population_50x50,
          color = "gray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_inflation), st_coordinates(accessibility_inflation)),
            aes(x = X, y = Y, fill = accessibility_inflation)) +
  scale_fill_distiller(name = "Inflation of accessibility",
                       palette = "PuRd", 
                       direction = 1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", 
                   width_hint = 0.4,
                   pad_x = unit(0.4, "in"), 
                   pad_y = unit(0.2, "in"),) +
  annotation_north_arrow(location = "tr", 
                         which_north = "true", 
        pad_x = unit(0.0, "in"), 
        pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)
```

@@

bi_map_3_all <- ggplot() +
  geom_sf(data = data_map %>%
            st_buffer(dist = 25, endCapStyle = "SQUARE"),
          mapping = aes(fill = bi_class), 
          color = NA,
          show.legend = FALSE) +
  geom_sf(data = cropped_da,
          fill = NA,
          color = "lightgrey") +
  geom_sf(data = sobi_service, 
          fill = NA,
          color = "blue") +
  ggtitle("All stations") +
  bi_scale_fill(pal = "GrPink", 
                dim = 3) +
  #annotation_scale(location = "bl", width_hint = 0.4,
  #                 pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in")) +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        plot.margin = unit(c(0, 0, 0, 0), "cm"),
        plot.title = element_text(hjust=0.5))

@@

\textcolor{blue}{Finally, it is important to note that this study examined accessibility to docking stations, that is, the entry point to the bikeshare system. There is a literature that examines transportation modes from this perspective, including accessibility to transit [e.g.,zhaoforecasting2003; @olszewskiusing2005; zieltracomparative2011] and more recently accessibility to bikeshare systems [e.g., @hosfordWhoArePublic2018; @mooneyFreedomStationSpatial2019; @caggianiequity2020; @duranfair2020]. These focus of these studies is to assess who has access to a transportation service. However, as argued by @moniruzzamanaccessibility2012, usage of the system likely depends as well on the accessibility to destinations that the system generates. An extension of the present study would be to investigate accessibility by the bikeshare system, and perhaps compare that to usage patterns.}
